

\newglossaryentry{abstract factory}{
    name={abstract factory},
    description={\citeauthor{gamma:1993} describe a design pattern in their book "Design Patterns" that can be applied to this problem.
    An abstract factory helps "creating families of related or dependent objects without specifying their concrete class"\citep[p.~99]{gamma:1993}.}
}

\newglossaryentry{amazon.com}{
    name={Amazon.com},
    description={One of the biggest internet based retailers in the world with focus electronic commerce and cloud computing.}
}

\newglossaryentry{dynamic programming}{
    name={dynamic programming},
    description={\color{red}TODO}
}

\newglossaryentry{e-commerce}{
    name={e-commerce},
    description={{\color{red}TODO}}
}

\newglossaryentry{eBay}{
    name={eBay},
    description={{\color{red}TODO}}
}

\newglossaryentry{json}{
    name={JSON},
    description={{\color{red}TODO JavaScript Object Notation}}
}

\newglossaryentry{rs}{
    name={RS},
    description={Abbreviation for recommender systems.}
}

\newglossaryentry{git}{
    name={git},
    description={\color{red}TODO}
}

\newglossaryentry{ir}{
    name={IR},
    description={Abbreviation for information retrieval.}
}

\newglossaryentry{nodejs}{
    name={node.js},
    description={\color{red}TODO}
}

\newglossaryentry{python}{
    name=Python,
    description={
        A widely used scripting language with focus on readable source-code.
    }
}

\newglossaryentry{pybottle}{
    name=bottle,
    description={
        A python based web-framework that supports routing, templates and contains a web-server.
    }
}

\newglossaryentry{sqlite3}{
    name=SQLite3,
    description={
        A relational database system with support of Transactions and Views. It is also included in one of the standard Python-modules.
    }
}

\newglossaryentry{sphinx}{
    name=Sphinx,
    description={
        A document generator initially built for Python. It creates a documentation from docstrings within the Python source code.
    }
}

\newglossaryentry{web api}{
    name={web API},
    description={\color{red}TODO}
}

\newglossaryentry{zalando}{
    name={Zalando},
    description={A online shop specialized on clothing}
}
